### 2023-09-03 sections/3-datasets.tex

We benchmark on a variety of datasets from the ann-benchmarks suite~\cite{Aumller2018ANNBenchmarksAB}, 
listed below, along with the appropriate distance function.
Table~\ref{table:datasets:summary} summarizes the properties of these datasets.

>>>>

We benchmark on a variety of datasets from the ann-benchmarks suite~\cite{Aumller2018ANNBenchmarksAB}, 
along with the appropriate distance function.
Table~\ref{table:datasets:summary} summarizes the properties of these datasets.

The specifications for the machines used in benchmarking are as follows:

\begin{itemize}
\item Ark: 28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM, Manjaro Linux with kernel 5.15.78-1-MANJARO \#1 SMP PREEMPT. Rust 1.70, Python 3.10.5
\item Amazon AWS: 64-core Intel Xeon Platinum 8375C CPU 2.90GHz, 512GB RAM, Ubuntu 22.04.3-Ubuntu SMP. Rust 1.71.1, Python 3.10.12
\end{itemize}
